### 2023-06-29 2023/certificates/input_for_certificates.tex
certificates remove solver without members, experimental divisions

\MakeOnePage{Bitwuzla}{}{\withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{QF\_Bitvec}{\seq,\paral,\sat,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}}{\withtrack{QF\_UFBV}{\inc}, \withtrack{AUFBV}{\seq,\paral,\unsat,\fast}, \withtrack{AUFBVFP}{\seq,\paral,\unsat,\fast}, \withtrack{UFBV}{\unsat,\fast}}

@@

\MakeOnePage{OpenSMT}{}{\withtrack{QF\_LinearIntArith}{\seq,\paral}, \withtrack{QF\_LinearRealArith}{\inc,\mv\seq,\mv\paral}}{\withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_UFLIA}{\unsat}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}}

@@

\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv\seq,\mv\paral}, \withtrack{Largest Contribution}{\mv\seq,\mv\paral}}{\withtrack{QF\_LinearIntArith}{\sat,\mv\seq,\mv\paral}, \withtrack{QF\_NonLinearIntArith}{\unsat}, \withtrack{QF\_NonLinearRealArith}{\sat}}{\withtrack{QF\_IDL}{\seq,\paral,\unsat}}

@@

\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral}}{\withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\seq,\uc\paral}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc\seq}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral}, \withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat}, \withtrack{Bitvec}{\seq,\paral,\sat,\unsat,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_LinearRealArith}{\unsat}}{\withtrack{QF\_IDL}{\uc\seq,\uc\paral}, \withtrack{QF\_UFNIA}{\inc,\uc\seq,\uc\paral}, \withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\inc,\uc\seq,\uc\paral}, \withtrack{LIA}{\sat,\fast}, \withtrack{UFDT}{\fast}, \withtrack{QF\_UFLRA}{\uc\seq,\uc\paral}, \withtrack{QF\_BVFPLRA}{\unsat,\inc}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_NIRA}{\unsat}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_AUFLIA}{\uc\seq,\uc\paral}, \withtrack{QF\_UFNRA}{\inc,\uc\seq,\uc\paral}, \withtrack{BVFP}{\seq,\paral,\sat}}

@@

\MakeOnePage{Yices2}{}{\withtrack{QF\_LinearIntArith}{\fast,\inc,\uc\seq,\uc\paral}, \withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc\seq,\uc\paral,\mv\seq,\mv\paral}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\sat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearIntArith}{\fast}, \withtrack{QF\_Equality+LinearArith}{\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_Equality+Bitvec}{\inc}}{\withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv\seq,\mv\paral}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{QF\_UFLIA}{\seq,\paral,\sat,\inc,\mv\seq,\mv\paral}, \withtrack{QF\_UFLRA}{\seq,\paral,\inc,\mv\seq}, \withtrack{QF\_UFBV}{\sat}, \withtrack{QF\_UFIDL}{\seq,\paral}, \withtrack{QF\_RDL}{\unsat,\mv\seq,\mv\paral}, \withtrack{QF\_ALIA}{\seq,\paral,\sat}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat}, \withtrack{QF\_AUFBV}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{QF\_UFNRA}{\seq,\paral,\sat,\unsat,\fast}}

@@

\MakeOnePage{Vampire}{\withtrack{Biggest Lead}{\cloud}}{\withtrack{Equality}{\fast,\uc\paral,\cloud}, \withtrack{Equality+NonLinearArith}{\cloud}, \withtrack{Arith}{\cloud}, \withtrack{Equality+LinearArith}{\cloud}}{\withtrack{AUFLIA}{\unsat,\fast}, \withtrack{UFLIA}{\uc\paral}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{UFDTLIA}{\fast,\uc\seq,\uc\paral}, \withtrack{AUFNIRA}{\seq,\paral,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{UFNIA}{\uc\paral}, \withtrack{AUFLIRA}{\fast}}

@@

\MakeOnePage{SMTS portfolio}{}{\withtrack{QF\_LinearRealArith}{\cloud}}{}
\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_ABVFPLRA}{\sat,\fast}}
\MakeOnePage{UltimateEliminator+MathSAT}{}{\withtrack{Equality+MachineArith}{\inc}}{\withtrack{BVFPLRA}{\unsat}}

@@

\MakeOnePage{-}{}{\withtrack{FPArith}{\uc\seq,\uc\paral}, \withtrack{QF\_Equality+LinearArith}{\cloud}}{\withtrack{AUFLIRA}{\sat,\cloud}, \withtrack{QF\_RDL}{\cloud}, \withtrack{UFDTNIA}{\sat}, \withtrack{AUFBVDTNIRA}{\sat}, \withtrack{UFDTNIRA}{\sat}, \withtrack{QF\_AUFBVFP}{\unsat}, \withtrack{AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc\seq,\uc\paral}, \withtrack{UFDTLIA}{\sat,\cloud}, \withtrack{UFBVFP}{\sat}, \withtrack{QF\_NIRA}{\sat,\fast}, \withtrack{AUFBVDTNIA}{\sat}, \withtrack{QF\_SNIA}{\unsat}, \withtrack{AUFBVFP}{\sat}, \withtrack{QF\_LIRA}{\uc\seq,\uc\paral}, \withtrack{ABVFP}{\uc\seq,\uc\paral}, \withtrack{ABVFPLRA}{\uc\seq,\uc\paral}, \withtrack{QF\_UFDT}{\fast}, \withtrack{AUFFPDTNIRA}{\sat}, \withtrack{QF\_UFFP}{\uc\seq,\uc\paral}, \withtrack{UFBVLIA}{\sat,\fast}, \withtrack{AUFDTNIRA}{\sat,\cloud}, \withtrack{AUFDTLIRA}{\sat}, \withtrack{UFLRA}{\sat}}
\MakeOnePage{cvc5-cloud}{}{}{\withtrack{UFDTNIRA}{\cloud}, \withtrack{QF\_IDL}{\cloud}, \withtrack{AUFDTLIRA}{\cloud}, \withtrack{NRA}{\cloud}, \withtrack{UFDTLIRA}{\cloud}}
\MakeOnePage{smtinterpol}{\withtrack{Biggest Lead}{\inc}}{\withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv\seq,\mv\paral}, \withtrack{QF\_Equality+NonLinearArith}{\inc,\uc\seq,\uc\paral}, \withtrack{QF\_NonLinearIntArith}{\inc}, \withtrack{QF\_Datatypes}{\fast}}{\withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{ALIA}{\seq,\paral,\sat,\fast}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ALIA}{\uc\seq,\uc\paral}, \withtrack{UFLIA}{\sat}, \withtrack{QF\_UF}{\uc\paral}, \withtrack{AUFDTLIA}{\uc\seq,\uc\paral}, \withtrack{UFDTLIRA}{\uc\seq,\uc\paral}}

@@

\MakeOnePage{veriT}{}{}{\withtrack{UFLIA}{\fast}, \withtrack{UFLRA}{\seq,\paral,\unsat,\fast}}

@@

\MakeOnePage{SMTS cube-and-conquer (fixed)}{}{\withtrack{QF\_LinearIntArith}{\cloud}}{}

@@

\MakeOnePage{Z3str4}{}{}{\withtrack{QF\_S}{\unsat}}

@@

\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\unsat,\fast}}{}

>>>>

\MakeOnePage{COLIBRI}{}{}{\withtrack{QF\_FP}{\unsat,\fast}, \withtrack{QF\_FPLRA}{\unsat,\fast}, \withtrack{QF\_ABVFPLRA}{\seq,\paral,\unsat,\fast}}

@@

\MakeOnePage{Z3++}{\withtrack{Biggest Lead}{\mv}, \withtrack{Largest Contribution}{\mv}}{\withtrack{QF\_LinearIntArith}{\seq,\paral,\sat,\mv}, \withtrack{QF\_NonLinearIntArith}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_NonLinearRealArith}{\seq,\paral,\sat}}{\withtrack{QF\_IDL}{\unsat}}

@@

\MakeOnePage{OSTRICH}{}{}{\withtrack{QF\_S}{\seq,\paral,\unsat}}

@@

\MakeOnePage{SMTInterpol}{\withtrack{Biggest Lead}{\fast}}{\withtrack{QF\_Datatypes}{\fast,\uc\textsuperscript\paral}, \withtrack{QF\_Equality+LinearArith}{\seq,\paral,\sat,\inc,\mv}, \withtrack{QF\_NonLinearIntArith}{\inc}}{\withtrack{QF\_UFDT}{\uc\textsuperscript\seq}, \withtrack{QF\_UFDTLIA}{\unsat,\fast,\uc}, \withtrack{QF\_LIA}{\unsat}, \withtrack{QF\_AUFNIA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{ALIA}{\sat,\uc}, \withtrack{QF\_ANIA}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_ALIA}{\uc}, \withtrack{UFLIA}{\sat}, \withtrack{QF\_UF}{\uc\textsuperscript\paral}, \withtrack{UFIDL}{\sat}, \withtrack{AUFDTLIA}{\uc}}

@@

\MakeOnePage{Bitwuzla}{\withtrack{Biggest Lead}{\inc}}{\withtrack{QF\_Bitvec}{\inc}, \withtrack{QF\_FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc}, \withtrack{FPArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_Equality+Bitvec}{\seq,\paral,\sat,\unsat,\fast,\inc,\mv}, \withtrack{Equality+MachineArith}{\inc}, \withtrack{Bitvec}{\sat}}{\withtrack{QF\_ABVFPLRA}{\uc}, \withtrack{ABVFP}{\sat,\fast}, \withtrack{AUFBV}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_ABVFP}{\uc}, \withtrack{QF\_BVFPLRA}{\uc}, \withtrack{QF\_BVFP}{\uc}, \withtrack{ABVFPLRA}{\fast}, \withtrack{UFBVFP}{\seq,\paral,\unsat}, \withtrack{AUFBVFP}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{UFBV}{\seq,\paral,\sat,\unsat,\fast}}

@@

\MakeOnePage{Vampire}{}{\withtrack{Equality}{\fast}}{\withtrack{UFDTNIA}{\seq,\paral,\unsat,\fast,\uc}, \withtrack{AUFLIA}{\unsat,\fast}, \withtrack{ALIA}{\seq,\paral,\unsat,\fast}, \withtrack{UFDTLIA}{\fast,\uc}, \withtrack{AUFNIRA}{\paral,\unsat,\fast}, \withtrack{UF}{\seq,\paral,\sat}, \withtrack{AUFLIRA}{\fast}}

@@

\MakeOnePage{Yices2}{}{\withtrack{QF\_LinearIntArith}{\fast,\inc,\uc}, \withtrack{QF\_Equality+Bitvec}{\uc}, \withtrack{QF\_Equality}{\seq,\paral,\sat,\unsat,\fast,\uc,\mv}, \withtrack{QF\_LinearRealArith}{\seq,\paral,\fast,\uc}, \withtrack{QF\_Bitvec}{\uc}, \withtrack{QF\_Equality+LinearArith}{\fast,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\sat}}{\withtrack{QF\_LIRA}{\seq,\paral,\sat,\unsat,\mv}, \withtrack{QF\_UFLIA}{\unsat,\inc}, \withtrack{QF\_AUFBV}{\fast}, \withtrack{QF\_AUFBVLIA}{\inc}, \withtrack{QF\_UFLRA}{\seq,\paral,\sat,\unsat,\inc,\mv}, \withtrack{QF\_UFNRA}{\seq,\paral,\unsat,\fast,\inc,\mv}, \withtrack{QF\_UFBVLIA}{\inc}, \withtrack{QF\_RDL}{\sat,\unsat,\mv}, \withtrack{QF\_ALIA}{\unsat}, \withtrack{QF\_AUFLIA}{\seq,\paral,\sat,\unsat}}

@@

\MakeOnePage{STP}{}{\withtrack{QF\_Bitvec}{\seq,\paral,\sat,\unsat,\fast,\mv}}{}

@@

\MakeOnePage{cvc5}{\withtrack{Biggest Lead}{\seq,\paral,\sat,\unsat,\uc}, \withtrack{Largest Contribution}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}}{\withtrack{QF\_LinearIntArith}{\unsat}, \withtrack{QF\_Strings}{\seq,\paral,\sat,\unsat}, \withtrack{QF\_Datatypes}{\seq,\paral,\sat,\unsat,\uc\textsuperscript\seq}, \withtrack{Equality+MachineArith}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{Equality}{\seq,\paral,\sat,\unsat,\inc,\uc}, \withtrack{Equality+LinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{Arith}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{QF\_Equality+NonLinearArith}{\seq,\paral,\unsat,\fast,\inc,\uc}, \withtrack{Bitvec}{\seq,\paral,\unsat,\inc,\uc}, \withtrack{QF\_Equality+Bitvec+Arith}{\inc}, \withtrack{Equality+NonLinearArith}{\seq,\paral,\sat,\unsat,\fast,\inc,\uc}, \withtrack{QF\_FPArith}{\uc}, \withtrack{QF\_NonLinearRealArith}{\unsat,\fast}, \withtrack{QF\_Equality}{\inc}, \withtrack{QF\_LinearRealArith}{\unsat}}{\withtrack{QF\_FP}{\sat,\mv}, \withtrack{QF\_IDL}{\uc}, \withtrack{QF\_UFNIA}{\sat}, \withtrack{LIA}{\sat,\fast}, \withtrack{UFDT}{\fast}, \withtrack{QF\_UFLRA}{\uc}, \withtrack{NIA}{\sat,\fast}, \withtrack{QF\_UFDTLIRA}{\seq,\paral,\sat,\unsat,\fast,\uc}, \withtrack{QF\_ALIA}{\inc}, \withtrack{QF\_NIRA}{\seq,\paral,\unsat}, \withtrack{QF\_UFBVDT}{\seq,\paral,\sat,\unsat,\fast}, \withtrack{QF\_AUFLIA}{\uc,\mv}, \withtrack{QF\_BVFPLRA}{\inc}, \withtrack{QF\_AX}{\mv}}

@@

\MakeOnePage{OpenSMT}{}{\withtrack{QF\_LinearRealArith}{\sat,\inc,\mv}, \withtrack{QF\_Equality+LinearArith}{\unsat}}{\withtrack{QF\_LIA}{\seq,\paral}, \withtrack{QF\_LRA}{\seq,\paral,\unsat,\fast}, \withtrack{QF\_UFIDL}{\seq,\paral,\sat,\mv}}

@@

\MakeOnePage{z3-alpha}{}{\withtrack{QF\_Strings}{\fast}}{\withtrack{QF\_S}{\sat}, \withtrack{QF\_SNIA}{\seq,\paral,\sat}}

@@

\MakeOnePage{iProver}{}{}{\withtrack{ANIA}{\unsat}}
